Deciding to Disclose

### 2015-06-04 Model.tex
Add CPT eg to ipython
And start correcting missing part of CPT in paper

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} &= \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} &= \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
R_{w}(l, l) &= -10
\end{align}
\end{equation}

@@

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate the `prospects'\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} of more than two actions. \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

@@

and $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss, and \(\lambda\) is a multiplier giving the aversion to loss. The \ac{CPT} value of outcome $u_{i}$, occurring with probability \(p\) is $v(u_{i})w^{+}(p)$
if $u_{i}\geq0$, and $v(u_{i})w^{-}(p)$ otherwise. For any given action the \ac{CPT}
value is the sum of the value of the prospects of that action, as
in the Bayesian risk model, and the agent chooses the option which maximises this quantity.

>>>>

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
u_{w}(l, i, l, j) &= 10\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
R_{w}(l, l) &= -10
\end{align*}
\end{equation*}

@@

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate the `prospects'\footnote{Where a prospect is a sequence of payoff-probability pairings in ascending order of payoff, associated with an action.} of more than two actions. \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

@@

and $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.

Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,

\begin{equation}
\pi_{n}^{+}=w^{+}(p_{n})
\end{equation}
\begin{equation}
\pi_{-m}^{-}=w^{-}(p_{-m})
\end{equation}
\begin{equation}
\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
\end{equation}
\begin{equation}
\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
\end{equation}

The \ac{CPT} value of outcome $u_{i}$, occurring with probability \(p\) is $v(u_{i})\pi^{+}(p_{i})$
if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
value is the sum of the value of the prospects of that action, as
in the Bayesian risk model, and the agent chooses the option which maximises this quantity.

Once again, we return to the light drinker example.  The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$. For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.

\begin{equation*}
\begin{align*}
\alpha &= 0.88\\
\gamma &= 0.61\\
p(l) &= \frac{1}{6}\\
p(m) &= \frac{1}{6}\\
p(h) &= \frac{2}{3}\\
p(r | l) &= \frac{1}{4}\\
p(n | l) &= \frac{3}{4}\\
u_{w}(l, i, l, j) &= 10\\
v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
v(u_{w}) &= 10^{0.88} = 7.59\\
w^{+}(p(l)p(r | l))  &= \frac{(p(l)p(r | l))^\gamma}{[(p(l)p(r | l))^\gamma + (1-(p(l)p(r | l)))^\gamma]^\frac{1}{\gamma}}\\
w^{+}(p(l)p(r | l))  &= \frac{\frac{1}{24}^{0.61}}{[\frac{1}{24}^{0.61} + (1-\frac{1}{24})^{0.61}]^\frac{1}{0.61}} = 0.12\\
w^{+}(p(l)p(n | l)) &= \frac{\frac{1}{8}^{0.61}}{[\frac{1}{8}^{0.61} + (1-\frac{1}{8})^{0.61}]^\frac{1}{0.61}} = 0.21\\
w^{+}(p(m)p(r | l)) &= 0.12\\
w^{+}(p(m)p(n | l)) &= 0.21\\
w^{+}(p(h)p(r | l)) &= 0.24\\
w^{+}(p(h)p(n | l)) &= 0.42\\
V(l) &= 0.12\cdot7.59 + 0.21\cdot7.59 + 0.12\cdot7.59 + 0.21\cdot7.59 + 0.24\cdot7.59 + 0.42\cdot7.59 &= 10.02
\end{align*}
\end{equation*}
